quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-12 paper-quollr.Rmd
Updated the dataset table

```{r}
datasets_tb <- tibble(dt = c("scurve",
                             "scurve_umap",
                             "scurve_umap_predict",
                             "scurve_umap2",
                             "scurve_umap3",
                             "scurve_umap4",
                             "scurve_umap5",
                             "scurve_umap6",
                             "scurve_model_obj",
                             "scurve_umap_mse",
                             "scurve_umap_mse2",
                             "scurve_umap_mse3",
                             "scurve_umap_mse4",
                             "scurve_umap_mse5",
                             "scurve_umap_mse6"), 
                      text = c("Simulated data to generate a S-curve with additional noise dimensions.",
                             "The UMAP embedding with n_neighbors $46$ and min_dist $0.9$ for `S-curve`.",
                             "scurve_umap_predict",
                             "The UMAP embedding with n_neighbors $10$ and min_dist $0.4$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $62$ and min_dist $0.1$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $30$ and min_dist $0.5$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $15$ and min_dist $0.5$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $15$ and min_dist $0.1$ for `S-curve`.",
                             "scurve_model_obj",
                             "scurve_umap_mse",
                             "scurve_umap_mse2",
                             "scurve_umap_mse3",
                             "scurve_umap_mse4",
                             "scurve_umap_mse5",
                             "scurve_umap_mse6"))
```

>>>>

```{r}
datasets_tb <- tibble(dt = c("scurve",
                             "scurve_umap",
                             "scurve_umap_predict",
                             "scurve_umap2",
                             "scurve_umap3",
                             "scurve_umap4",
                             "scurve_umap5",
                             "scurve_umap6",
                             "scurve_model_obj",
                             "scurve_umap_mse",
                             "scurve_umap_mse2",
                             "scurve_umap_mse3",
                             "scurve_umap_mse4",
                             "scurve_umap_mse5",
                             "scurve_umap_mse6"), 
                      text = c("Simulated data to generate a S-curve with additional noise dimensions.",
                             "The UMAP embedding with n_neighbors $46$ and min_dist $0.9$ for `S-curve`.",
                             "The predicted UMAP embedding with n_neighbors $46$ and min_dist $0.9$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $10$ and min_dist $0.4$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $62$ and min_dist $0.1$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $30$ and min_dist $0.5$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $15$ and min_dist $0.5$ for `S-curve`.",
                             "The UMAP embedding with n_neighbors $15$ and min_dist $0.1$ for `S-curve`.",
                             "The object contains the scaled NLDR object (`nldr_obj`), the hexagonal object (`hb_obj`), the fitted model in both $2\\text{-}D$ (`model_2d`), and $p\\text{-}D$ (`model_highd`), and triangular mesh (`trimesh_data`).",
                             "The MSE corresponding to different binwidths for the model generated using `scurve_umap`.",
                             "The MSE corresponding to different binwidths for the model generated using `scurve_umap2`.",
                             "The MSE corresponding to different binwidths for the model generated using `scurve_umap3`.",
                             "The MSE corresponding to different binwidths for the model generated using `scurve_umap4`.",
                             "The MSE corresponding to different binwidths for the model generated using `scurve_umap5`.",
                             "The MSE corresponding to different binwidths for the model generated using `scurve_umap6`."))
```

### 2025-05-12 paper-quollr.tex
Updated the dataset table

\caption{\label{tab:datasets-tb-pdf}quollr data sets}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
data & explanation\\
\midrule
scurve & Simulated data to generate a S-curve with additional noise dimensions.\\
scurve\_umap & The UMAP embedding with n\_neighbors \$46\$ and min\_dist \$0.9\$ for `S-curve`.\\
scurve\_umap\_predict & scurve\_umap\_predict\\
scurve\_umap2 & The UMAP embedding with n\_neighbors \$10\$ and min\_dist \$0.4\$ for `S-curve`.\\
scurve\_umap3 & The UMAP embedding with n\_neighbors \$62\$ and min\_dist \$0.1\$ for `S-curve`.\\
\addlinespace
scurve\_umap4 & The UMAP embedding with n\_neighbors \$30\$ and min\_dist \$0.5\$ for `S-curve`.\\
scurve\_umap5 & The UMAP embedding with n\_neighbors \$15\$ and min\_dist \$0.5\$ for `S-curve`.\\
scurve\_umap6 & The UMAP embedding with n\_neighbors \$15\$ and min\_dist \$0.1\$ for `S-curve`.\\
scurve\_model\_obj & scurve\_model\_obj\\
scurve\_umap\_mse & scurve\_umap\_mse\\
\addlinespace
scurve\_umap\_mse2 & scurve\_umap\_mse2\\
scurve\_umap\_mse3 & scurve\_umap\_mse3\\
scurve\_umap\_mse4 & scurve\_umap\_mse4\\
scurve\_umap\_mse5 & scurve\_umap\_mse5\\
scurve\_umap\_mse6 & scurve\_umap\_mse6\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:datasets-tb-pdf}quollr data sets}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
data & explanation\\
\midrule
scurve & Simulated data to generate a S-curve with additional noise dimensions.\\
scurve\_umap & The UMAP embedding with n\_neighbors \$46\$ and min\_dist \$0.9\$ for `S-curve`.\\
scurve\_umap\_predict & The predicted UMAP embedding with n\_neighbors \$46\$ and min\_dist \$0.9\$ for `S-curve`.\\
scurve\_umap2 & The UMAP embedding with n\_neighbors \$10\$ and min\_dist \$0.4\$ for `S-curve`.\\
scurve\_umap3 & The UMAP embedding with n\_neighbors \$62\$ and min\_dist \$0.1\$ for `S-curve`.\\
\addlinespace
scurve\_umap4 & The UMAP embedding with n\_neighbors \$30\$ and min\_dist \$0.5\$ for `S-curve`.\\
scurve\_umap5 & The UMAP embedding with n\_neighbors \$15\$ and min\_dist \$0.5\$ for `S-curve`.\\
scurve\_umap6 & The UMAP embedding with n\_neighbors \$15\$ and min\_dist \$0.1\$ for `S-curve`.\\
scurve\_model\_obj & The object contains the scaled NLDR object (`nldr\_obj`), the hexagonal object (`hb\_obj`), the fitted model in both \$2\textbackslash{}text\{-\}D\$ (`model\_2d`), and \$p\textbackslash{}text\{-\}D\$ (`model\_highd`), and triangular mesh (`trimesh\_data`).\\
scurve\_umap\_mse & The MSE corresponding to different binwidths for the model generated using `scurve\_umap`.\\
\addlinespace
scurve\_umap\_mse2 & The MSE corresponding to different binwidths for the model generated using `scurve\_umap2`.\\
scurve\_umap\_mse3 & The MSE corresponding to different binwidths for the model generated using `scurve\_umap3`.\\
scurve\_umap\_mse4 & The MSE corresponding to different binwidths for the model generated using `scurve\_umap4`.\\
scurve\_umap\_mse5 & The MSE corresponding to different binwidths for the model generated using `scurve\_umap5`.\\
scurve\_umap\_mse6 & The MSE corresponding to different binwidths for the model generated using `scurve\_umap6`.\\
\bottomrule
\end{tabular}
\end{table}
